Exploring dimensions of biodiversity in Japanese ferns

### 2021-05-19 ms/manuscript.Rmd
Update MS

We constructed a set of linear models for each response variable (richness, SES of PD, SES of FD, SES of RPD, SES of RFD, PE p-score) as dependent on all possible combinations of environmental variables (temperature, precipitation, and precipitation seasonality). Initial inspection of the relationship between richness and temperature showed a hump-shaped pattern, so we also included a quadratic term for temperature for the richness model only. We fit models including a Matérn correlation matrix based on the geographic centroids of each grid cell with the R package spaMM [@Rousset2014], then identified the best-fitting model for each response variable as the one with the greatest log-likelihood. We verified the significance of each term of the best model by conducting likelihood ratio tests (LRTs) between the full model and models each with a single term of interest removed, in sequence. We also verified the significance of the full model relative to the null model (only including the Matérn correlation matrix) using LRTs.

To compare between the models fit using temperature (environmental model) vs. % apomictic taxa (reproductive model) in response variables with a genetic component (SES of PD, SES of RPD, PE p-score), we constructed additional models where % apomictic taxa was used in place of temperature in the best-fitting model for each response variable. We then conducted LRTs between the environmental model vs. the reproductive model, as well as between the full reproductive model and models with each term of interest removed, and between the full reproductive model vs. the null model.

>>>>

We constructed a linear model for each response variable (richness, SES of PD, SES of FD, SES of RPD, SES of RFD, PE p-score) dependent on all environmental variables (temperature, precipitation, and precipitation seasonality). We did not include any interaction terms as we had no a-priori reason to do so. Initial inspection of the relationship between richness and temperature showed a hump-shaped pattern, so we also included a quadratic term for temperature for the richness model only. We fit models including a Matérn correlation matrix based on the geographic centroids of each grid cell with the R package spaMM [@Rousset2014]. We verified the significance of each term of the model by conducting likelihood ratio tests (LRTs) between the full model and models each with a single term of interest removed, in sequence. We also verified the significance of the full model relative to the null model (only including the Matérn correlation matrix) using LRTs.

To compare between the models fit using temperature (environmental model) vs. % apomictic taxa (reproductive model) in response variables with a genetic component (SES of PD, SES of RPD, PE p-score), we constructed additional models where % apomictic taxa was used in place of temperature. We then conducted LRTs as described above, as well as between the environmental model vs. the reproductive model.
